### 2018-02-02 README.Rmd
add more to contribuging documentat and link to from readme, #635
changed coc file name

@@

* Please [report any issues or bugs](https://github.com/ropensci/taxize/issues).
* License: MIT
* Get citation information for `taxize` in R doing `citation(package = 'taxize')`
* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.

>>>>

## Contributing

See our [CONTRIBUTING](.github/CONTRIBUTING.md) document.

@@

* Please [report any issues or bugs](https://github.com/ropensci/taxize/issues).
* License: MIT
* Get citation information for `taxize` in R doing `citation(package = 'taxize')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
